Particle Interception as a Function of Reynolds Number and Collector Density

### 2021-01-09 code/analysis.Rmd
added some plots based on k_c and k_s

final %>%
  filter(dowel_density != "0000") %>%
  ggplot(aes(x = Re, y = k_c, ymin = k_c - dk_c, ymax = k_c + dk_c, color = as.character(round(ad,5)))) +
  geom_line(lty = "dotted", size = 2, alpha = .3) + 
  geom_point(position = position_dodge(width = 10)) +
  geom_errorbar(width = 10, position = "dodge") +  
  scale_color_manual(values = c("blue","green","red")) +
  scale_y_continuous(labels = function(x) format(x, scientific = TRUE)) +
  labs(y = expression(paste(italic(k[c])," (",s^{-1},")")), x = expression(Re[c]), color = expression(italic(ad))) +
  theme_minimal()
```

>>>>

final %>%
  filter(dowel_density != "0000") %>%
  ggplot(aes(x = Re, y = k_c, ymin = k_c - dk_c, ymax = k_c + dk_c, color = as.character(round(ad,5)))) +
  geom_line(lty = "dotted", size = 2, alpha = .3) + 
  geom_point(position = position_dodge(width = 10)) +
  geom_errorbar(width = 10, position = "dodge") +  
  scale_color_manual(values = c("blue","green","red")) +
  scale_y_continuous(labels = function(x) format(x, scientific = TRUE)) +
  labs(y = expression(paste(italic(k[c])," (",s^{-1},")")), x = expression(Re[c]), color = expression(italic(ad))) +
  theme_minimal()

final %>%
  filter(dowel_density != "0000") %>%
  ggplot(aes(x = Re, y = k_c/(k_s+k_c), color = as.character(round(ad,5)))) +
  geom_line(lty = "dotted", size = 2, alpha = .3) + 
  geom_point(position = position_dodge(width = 10)) +
  scale_color_manual(values = c("blue","green","red")) +
  theme_minimal()

final %>%
  filter(dowel_density != "0000") %>%
  ggplot(aes(x = Re, y = k_s+k_c, color = as.character(round(ad,5)))) +
  geom_line(lty = "dotted", size = 2, alpha = .3) + 
  geom_point(position = position_dodge(width = 10)) +
  scale_color_manual(values = c("blue","green","red")) +
  theme_minimal()
